---
title: "Week 1 Exercizes"
author: "Luke Tuttle"
date: "5/16/18"
output: "pdf_document"
---

This is an R Markdown of the exercizes assigned for week 1 of R training at Sorneson Impact Center. 


```{r, setup, include=FALSE}

library(tidyverse)
library(knitr)
library(forcats)
library(readxl)
library(lubridate)

```

Exercize Assignment
+ Create table of the number of cars by gear
+ Create table of the number of cars by carb
+ Create a table of vs
+ Create a table of am
+ Create a table of cyl by gear
+ Create a table of cyl by am
+ Create a table of cyl by vs
+ Create a histogram of wt
+ using geom_histogram()
+ Don’t need to count, just pass the dataset to
  ggplot
+ Don’t specify a y, only the x
+ Create a histogram of mpg
+ Create a histogram of qsec
+ Create a histogram of hp
+ Create a table of mean mpg by cyl
+ Graph mean mpg by cyl
+ x=cyl, y=meanmpg
+ Create a table of mean wt by cyl
+ Graph mean wt by cyl
+ x=cyl, y=meanwt
+ Create a table of mean hp by cyl
+ Graph mean hp by cyl
+ x=cyl, y=meanhp
+ Do any other exploratory analysis that
interests you


Tables 1-7
```{r, tables}



mtcars %>% 
  group_by(gear) %>% 
  summarize(n = n())

mtcars %>% 
  group_by(carb) %>% 
  summarize(n = n())

#Create a table of vs
#Create a table of am

#tables of cyl by "x" 
with(mtcars,table(gear, cyl))

with(mtcars,table(am, cyl))

with(mtcars,table(vs, cyl))

```


Histograms of wt, mpg, qsec, and hp. 
```{r, histograms}
#histogram of wt
ggplot(mtcars, aes(x = wt)) +
  geom_histogram(binwidth = .25)

#histogram of mpg
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = 3)

#histogram of qsec
ggplot(mtcars, aes(x = qsec)) +
  geom_histogram(binwidth = 0.5)

#histogram of hp
ggplot(mtcars, aes(x = hp)) +
  geom_histogram(binwidth = 25)

```

Mean mpg by cylinder 
```{r, mean_mpg_by_cyl}

mtcars %>%
  group_by(cyl) %>% 
  summarize(meanmpg = mean(mpg))

#graph
mtcars %>%
  group_by(cyl) %>% 
  summarize(meanmpg = mean(mpg)) %>% 
ggplot(aes(x = cyl, y = meanmpg)) + 
    geom_col()

```

Mean weight by cylinder
```{r, wt_by_cyl}

wt_cyl <- mtcars %>%
  group_by(cyl) %>% 
  summarize(meanwt = mean(wt))

ggplot(wt_cyl, aes(x = cyl, y = meanwt)) +
  geom_col(width = 1)

```

Mean horsepower by cylinder
```{r, hp_by_cyl}

meanhp_cyl <- mtcars %>% 
  group_by(cyl) %>% 
  summarize(meanhp = mean(hp))

ggplot(meanhp_cyl, aes(x = cyl, y = meanhp)) +
  geom_col(width = 1)
```





 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

