---
title: "Week 1 Exercizes"
author: "Luke Tuttle"
date: "5/16/18"
output: pdf_notebook
---

This is an R Markdown of the exercizes assigned for week 1 of R training at Sorneson Impact Center. 


```{r, setup, include=FALSE}

library(tidyverse)
library(knitr)
library(forcats)
library(readxl)
library(lubridate)

```

Tables 1-7
```{r, tables}



mtcars %>% 
  group_by(gear) %>% 
  summarize(n = n())

mtcars %>% 
  group_by(carb) %>% 
  summarize(n = n())

#Create a table of vs
#Create a table of am

#tables of cyl by "x" 
with(mtcars,table(gear, cyl))

with(mtcars,table(am, cyl))

with(mtcars,table(vs, cyl))

#histogram of wt
ggplot(mtcars, aes(x = wt)) +
  geom_histogram(binwidth = .25)

#histogram of mpg
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(binwidth = .25)

#histogram of qsec
ggplot(mtcars, aes(x = qsec)) +
  geom_histogram(binwidth = .25)

#histogram of hp
ggplot(mtcars, aes(x = hp)) +
  geom_histogram(binwidth = .25)

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

